---
title       : Developing Data Products Project Presentation
subtitle    : Slidify + Shiny
author      : Ishan Kapoor
job         : Developing Data Products
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [shiny, interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
ext_widgets : {rCharts: [libraries/nvd3]}
---


## Course Project : Sliders

- Project is available at [https://ikapoor-devdataprod.shinyapps.io/ikapoor-devdataprod](https://ikapoor-devdataprod.shinyapps.io/ikapoor-devdataprod)
- Below is a screnshot of the application.

<img src=project.jpg></img>

---

## Course Project : Sliders


  
  - Project has custom format of slider scale ($)

  - Has various slider types for input

  - Has reactive <code>code</code> Which computes the sum of Integer and Decimal.

---


## Interactive Charts

- Example of some fancy rCharts within Slidify

```{r echo = F, results = 'asis'}
require(rCharts)
haireye = as.data.frame(HairEyeColor)
n1 <- nPlot(Freq ~ Hair, group = 'Eye', type = 'multiBarChart',
            data = subset(haireye, Sex == 'Male'))
n1$print('chart1')
```

---

### Simple R code

-Some rather simple R code executed within Slidify


```{r}
a <- 42
A <- a * 2
print(A)
```





